Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-11-24 paper/manuscript.Rmd
Redo first paragraph discussiojn

Our results suggest that community context plays a central role in determining the net cost or benefit of sharing pollinators.
<!-- DBS: In the intro, it's about net outcome. Here, it's about net cost or benefit. Which is it? -->
First, we found that pollinator sharing can lead to both net facilitative and net competitive effects to plant species in a community. 
Second, we found that multiple ecological factors can modulate the intensity of competition; however, conspecific and heterospecific pollen deposition are tightly coupled and this creates a clear trade-off between the quantity and purity of pollination [@thomson_effects_2019]. 
Third, we found that the way these factors influence competition is strongly shaped by the community context. 
That is, if these factors collectively define a species' pollination niche,
<!-- DBS: Yet another way to phrase this concept... -->
the same plant species can occupy dramatically different niches depending on the community to which it belongs.

The criterion we used to identify the effect of animal-mediated pollination suggested that neither facilitation nor competition are dominant in pollination communities.
A previous study showed that, in diverse pollination communities, sharing pollinators does not necessarily translate to net competition [@tur_evaluating_2016]. 
The overall extent of facilitation/competition of pollination communities can depend on factors like the adversity of the environment [@tur_evaluating_2016; @callaway_positive_2002] or how disturbances affect pollinator populations [@stavert_exotic_2017]. 
However, why some species experience more competition than others was not understood. 
Although we were unable to measure the fitness outcomes, here we show that the coexistence of facilitative and competitive effects of animal-mediated pollination can be at least partially explained by trade-offs in the pollination service--both the short and the long term. 
These trade-offs arise when plants simultaneously maximise the deposition of conspecific pollen and minimise that of heterospecific pollen.

In the short term, being a specialist and sharing no pollinators might reduce competition [@muchhala_competition_2010] and hence be preferable, not only due to costs to male fitness [@muchhala_interspecific_2012; @morales_interspecific_2008], but also because, as we show here, sharing pollinators reduces both the quantity and purity of the conspecific pollen deposited. 
However, over long periods of time, there could be a risk associated with a specialist plant having few pollinators [@ricketts_tropical_2004]. 
To ensure long-term survival, it is thus likely that plants also need to balance this risk with the costs of sharing pollinators [@aizen_specialization_2012]. 
One possible solution is to share pollinators *and* have original traits---as we show that trait originality is generally beneficial to pollen deposition and it is commonly thought that species that are further from others in trait space benefit from reduced competition. 
Yet, there are two possible caveats to this strategy that highlight the interrelatedness of the ecological factors. 
First, in a mutualism context, it is also possible that trait originality could come at the cost of being less ‘apparent’ to pollinators [@reverte_pollinators_2016]. 
Second, the negative relationship between originality and generalism  [@carvalheiro_potential_2014] has been shown to depend on plant abundance [@coux_linking_2016], with generalist species being able to also have original traits only when they are abundant enough to provide a valuable reward to make visiting worthwhile to pollinators.

>>>>

Our results suggest that community context plays a central role in determining the pollen deposition dynamics and ultimately the net cost or benefit of sharing pollinators.
First, we found that multiple ecological factors can modulate the quality of the pollination service; however, conspecific and heterospecific pollen deposition are tightly coupled and this creates a clear trade-off between the quantity and purity of pollination [@thomson_effects_2019]. 
Second, we found that the way these factors shape pollen deposition for a species could be dramatically different across communities. 
For instance, while in a particular community a plant species could show high levels of pollinator sharing and relatively low trait differentiation, the same species in another community can have relatively high trait differentiation and low levels of pollinator sharing. 
Our findings highlight that trade-offs can at least partially explain the coexistence of facilitative and competitive effects of animal-mediated pollination in the pollination service--both the short and the long term.

The trade-offs involved in attaining high-quality pollination service (and more broadly between facilitation and competition) are likely to arise when plants simultaneously maximise the deposition of conspecific pollen and minimise that of heterospecific pollen. 
In the short term, being a specialist and sharing no pollinators might reduce competition [@muchhala_competition_2010] and hence be preferable, not only due to costs to male fitness [@muchhala_interspecific_2012; @morales_interspecific_2008], but also because, as we show here, sharing pollinators reduces both the quantity and purity of the conspecific pollen deposited. 
However, over long periods of time, there could be a risk associated with a specialist plant having few pollinators [@ricketts_tropical_2004]. 
To ensure long-term survival, it is thus likely that plants also need to balance this risk with the costs of sharing pollinators [@aizen_specialization_2012]. 
One possible solution is to share pollinators *and* have original traits---as we show that trait originality is generally beneficial to pollen deposition and it is commonly thought that species that are further from others in trait space benefit from reduced competition. 
Yet, there are two possible caveats to this strategy that highlight the interrelatedness of the ecological factors. 
First, in a mutualism context, it is also possible that trait originality could come at the cost of being less ‘apparent’ to pollinators [@reverte_pollinators_2016]. 
Second, the negative relationship between originality and generalism  [@carvalheiro_potential_2014] has been shown to depend on plant abundance [@coux_linking_2016], with generalist species being able also to have original traits only when they are abundant enough to provide a valuable reward to make visiting worthwhile to pollinators.
